%Aplicar efecto de primera página
\fancyhead{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[R]{\thepage}

\begin{thebibliography}{X}
\bibitem{bib:paper_1} \textit{Aplicaciones de CHIP-8, una máquina virtual de finales de los 70, en los estudios actuales de Ingeniería Informática},
	\textit{N.C. Cruz, J.L. Redondo, J.D. Álvarez, Pilar Martínez Ortigosa}, 2019
\bibitem{bib:paper_2} \textit{Using the Game Boy Advance to teach computer systems and architecture},
	\textit{Ian Finlayson}, 2016
\bibitem{bib:arm} \textit{ARM}\textsuperscript{\textregistered},
	\textit{ARM7TDMI Technical Reference Manual (Revision: r4p1)}, 2004
\bibitem{bib:gbatek} \textit{Martin Korth},
	\textit{GBATEK-GBA/NDS Technical Info}. https://problemkaputt.de/gbatek.htm
\bibitem{bib:cowbite} \textit{Tom Happ},
	\textit{CowBite Virtual Harware Specifications}, Aug. 04, 2002.
\bibitem{bib:belogic} \textit{BELOGIC},
	\textit{The Audio Advance -Gameboy Advance Sound Resources.}
\bibitem{bib:tonc} \textit{J Vijn},
	\textit{Tonc v1.4.2}, Mar. 24, 2013.
\bibitem{bib:rodrigo} \textit{Rodrigo Copetti},
	\textit{Game Boy Advance Architecture | A Practical Analysis}, Aug. 18, 2019
\bibitem{bib:gbadev} \textit{gbadev team},
	\textit{Gameboy Advance Development.}
\bibitem{bib:ing_vid} \textit{A. Cuesta},
	\textit{Ingeniería de Videojuegos - Universidad Juan Carlos I}, 2020
\bibitem{bib:paper3} 	\textit{Camper, Brett Bennett}, \textit{Homebrew and the social construction of gaming : community, creativity, and legal context of amateur Game Boy Advance development}, 2005
\bibitem{bib:sharp} \textit{https://dev.to/abhinavmir/gameboy-everything-under-the-hood-1p0b}
\bibitem{bib:8080} \textit{http://kazojc.com/elementy\_czynne/IC/INTEL-8080A.pdf}
\bibitem{bib:gb_og} \textit{http://gameboy.mongenel.com/dmg/asmmemmap.html}
\bibitem{bib:gb_og_2} \textit{https://bgb.bircd.org/pandocs.htm}
\bibitem{bib:gb_palette} \textit{https://www.chibiakumas.com/z80/platform2.php\#LessonP17}
\bibitem{bib:paper_4} \textit{Plataforma de desarrollo digital basado en Game Boy Advancey laarquitectura ARM7},
	\textit{Jhon A. Esquivel, Norbey Marín Moreno, Fernando Martínez Santa}, 2012
\bibitem{bib:paper_5} \textit{Introducing Computer Programming via Gameboy Advance Homebrew},
	\textit{Gary Kacmarcik, Sylvie Giral Kacmarcik}, 2009
\bibitem{bib:paper6} \textit{How are Agile Methods and Practices Deployed in Video Game Development? A Survey into Finnish Game Studios},
	\textit{Jussi Koutonen, Mauri Leppänen}
\bibitem{bib:agile_course} Philip Tan, Richard Eberhardt, Sara Verrilli, and Andrew Grant. CMS.611J Creating Video Games. Fall 2014. Massachusetts Institute of Technology: MIT OpenCourseWare, https://ocw.mit.edu.
\bibitem{bib:aff_matrix} https://www.cs.utexas.edu/users/fussell/courses/cs384g-fall2011/lectures/lecture07-Affine.pdf
\bibitem{bib:algebra} Juan Antonio López Ramos, Juan Cuadra Díaz. Apuntes de Álgebra Lineal y Matemáticas Discreta - Almería curso 2020/21
\bibitem{bib:gba_manual} Nintendo\textsuperscript{\textregistered}.
	AGB Programming Manual (Version: 1.1). 2001.
\bibitem{bib:armv4_isa} https://faculty-web.msoe.edu/meier/ce1921/slidesets/isaarm-instructions.pdf
\end{thebibliography}
